QALY Comparison - Living Wage Intervention

### 2023-11-24 minos/testing/QALY_comparison_livingWage.Rmd
Fixed some typos in living wage QALY comparison script
Created a new script to handle upscaling to uk individual population size, however this crashes my PC so Im going to have to test it on arc. Forgive me John Hodrien...

@@

```{r}
intervention.cost(base = baseline,
                  base.name = 'baseline',
                  int = livWage,
                  int.name = 'livingWageIntervention',
                  int.label = 'Living Wage')
```

>>>>

# Number people Below Living Wage

```{r}
# Only need this for the baseline 2020 input data
base.num <- base %>%
  filter()
```

@@

```{r}
intervention.cost(base = base,
                  base.name = 'baseline',
                  int = wage,
                  int.name = 'livingWageIntervention',
                  int.label = 'LivingWage')
```
